title: "html_text"
format: 
  html:
    toc: true
    toc-location: left
editor: visual
---

TODO:

-   [ ] Basic means of rendering per API
-   [ ] Privacy Issues across APIs

# Background

As part of the Demo sales App, we'd love to have a tweet wall/embedded text centre to look more professional, where the tweets are [masonified](https://www.smashingmagazine.com/native-css-masonry-layout-css-grid/). Which could nowadays be done with `bslib::layout_column_wrap()`

e.g. [Gaden Buie's Conference App](https://gadenbuie.shinyapps.io/tweet-conf-dash/) would compliment the landscape nicely. [Conference App Repo](https://github.com/gadenbuie/tweet-conf-dash) [shinyThings](https://github.com/gadenbuie/shinyThings/blob/main/R/pager.R) For the pager on the tweet wall (or we'll end up with hundreds (or could filter/sample the plotly_selected))

Question of whether this should be top posts (by likes, engagements?), top by cosine/x to some query?

[Embedding via reddit](https://www.reddit.com/wiki/embeds/)

<blockquote class="reddit-embed-bq" style="height:316px" data-embed-height="597">

<a href="https://www.reddit.com/r/redditdev/comments/16tqlth/updating_api_user_setting_fields/">Updating API user setting fields</a><br> by<a href="https://www.reddit.com/user/pl00h/">u/pl00h</a> in<a href="https://www.reddit.com/r/redditdev/">redditdev</a>

</blockquote>

```{=html}
<script async="" src="https://embed.reddit.com/widgets.js" charset="UTF-8"></script>
```
Need to paste in the user and the id

# Utils

```{r}
style_embedding <- function(height=400) {
    start_div <- paste0('<div style="height:', height,'px; overflow-y: scroll;">')
    end_div <- '</div>'
    
    return(list(start_div = start_div, end_div = end_div))
}
```

# Reddit

```{r}
shiny::HTML('<blockquote class="reddit-embed-bq" style="height:316px" data-embed-height="597"><a href="https://www.reddit.com/r/redditdev/comments/16tqlth/updating_api_user_setting_fields/">Updating API user setting fields</a><br> by<a href="https://www.reddit.com/user/pl00h/">u/pl00h</a> in<a href="https://www.reddit.com/r/redditdev/">redditdev</a></blockquote><script async="" src="https://embed.reddit.com/widgets.js" charset="UTF-8"></script>')

r_pl <- "https://www.reddit.com/r/sales/comments/10x8sj9/even_gong_who_by_all_accounts_is_absolutely/j7rcv7m/"
```

```{r, extract_subreddit}
extract_subreddit <- function(permalink) str_extract(permalink, "/r/(\\w+)", group = 1)

r_sr <- extract_subreddit(r_pl)
```

```{r, reddit_embed_function}
extract_reddit_html <- function(url, subreddit) {
  
  embedding_style <- style_embedding(height = 800)
  html <- paste0(embedding_style$start_div, '<blockquote class="reddit-embed-bq" style="height:316px" data-embed-height="597"><a href="',
                 url, '">Link to post</a><br></a> in<a href="https://www.reddit.com/r/', subreddit, '">',
                 subreddit, '</a></blockquote><script async="" src="https://embed.reddit.com/widgets.js" charset="UTF-8"></script>',
                 embedding_style$end_div)
  
  return(HTML(html))
}

r_e_html <- extract_reddit_html(r_pl, r_sr)
```

```{r}
create_reddit_embed <- function(permalink){
  if(!grepl("reddit", permalink)) stop("Not a reddit link")
  
  subreddit <- extract_subreddit(permalink)
  
  reddit_html <- extract_reddit_html(permalink, subreddit)
  
  return(reddit_html)
}

r_e <- create_reddit_embed(r_pl)
bslib::layout_column_wrap(1/2, r_e, r_e, r_e, r_e, r_e, r_e)
```

# Instagram

Private accounts are a bit of a problem with the instagram API - can't render the images, so will want to add a check later. Same may be true of Twitter.

[Instagram Embed API Terms of Service](https://developers.facebook.com/terms)

```{r, instagram_template}
.tmp_insta <- HTML('<blockquote class="instagram-media" data-instgrm-permalink="https://www.instagram.com/p/C6z8MZetvvn/?utm_source=ig_web_copy_link/" data-instgrm-version="12" style=" background:#FFF; border:0; border-radius:3px; box-shadow:0 0 1px 0 rgba(0,0,0,0.5),0 1px 10px 0 rgba(0,0,0,0.1); margin: 1px; max-width:540px; min-width:326px; padding:0; width:99.375%; width:-webkit-calc(100% - 2px); width:calc(100% - 2px);">
      <div style="padding:16px;">
      </div>
    </blockquote>
    <script async defer src="//www.instagram.com/embed.js"></script>
  ')

create_instagram_embed <- function(permalink) {
  
  html <- paste0('<blockquote class="instagram-media" data-instgrm-permalink="',
                 permalink, '" data-instgrm-version="12" style=" background:#FFF; border:0; border-radius:3px; box-shadow:0 0 1px 0 rgba(0,0,0,0.5),0 1px 10px 0 rgba(0,0,0,0.1); margin: 1px; max-width:540px; min-width:326px; padding:0; width:99.375%; width:-webkit-calc(100% - 2px); width:calc(100% - 2px);">
      <div style="padding:16px;">
      </div>
    </blockquote>
    <script async defer src="//www.instagram.com/embed.js"></script>')
  return(HTML(html))

}

bslib::layout_column_wrap(1/3, .tmp_insta, .tmp_insta, .tmp_insta)
```

```{r}
i_pl <- "https://www.instagram.com/p/CpsCY26IhDW/"
# i_pl <- "https://www.instagram.com/p/CohLj4rycfo/" # Bad link - deleted/private
```

```{r}
#Embed instagram function:
get_instagram_blockquote <- function(permalink) {
  html <- paste0('<blockquote class="instagram-media" data-instgrm-permalink="',
                 permalink, '" data-instgrm-version="12" style=" background:#FFF; border:0; border-radius:3px; box-shadow:0 0 1px 0 rgba(0,0,0,0.5),0 1px 10px 0 rgba(0,0,0,0.1); margin: 1px; max-width:540px; min-width:326px; padding:0; width:99.375%; width:-webkit-calc(100% - 2px); width:calc(100% - 2px);">
      <div style="padding:16px;">
      </div>
    </blockquote>
    <script async defer src="//www.instagram.com/embed.js"></script>')
  return(HTML(html))
}

i_bq <- get_instagram_blockquote(i_pl)

bslib::layout_column_wrap(1/3, i_bq, i_bq, i_bq, i_bq, i_bq)

# Check if the permalink links to a blocked account or a deleted post
httr::GET(i_pl)
```

# Twitter

```{r}
library(stringr)
extract_source <- function(permalink) str_extract(permalink, "(\\w+)\\.com", group = 1)
extract_tweet_id <- function(permalink) str_extract(permalink, "status/(\\d+)", group = 1)
extract_tweet_screen_name <- function(permalink) str_extract(permalink, "twitter.com/(\\w+)", group = 1)
extract_tweet_status <- function(permalink) str_extract(permalink, "status/(\\d+)", group = 1)

t_pl <- "https://twitter.com/dilekarasoy/status/1637074142615805952"
```

These functions do the work in the tweet conf app:

```{r,tweet_blockquote eval = FALSE}
get_tweet_blockquote <- function(screen_name, status_id, ..., null_on_error = TRUE, theme = "light") {
  oembed <- list(...)$oembed
  if (!is.null(oembed) && !is.na(oembed)) return(unlist(oembed))
  oembed_url <- glue::glue("https://publish.twitter.com/oembed?url=https://twitter.com/{screen_name}/status/{status_id}&omit_script=1&dnt=1&theme={theme}")
  bq <- purrr::possibly(httr::GET, list(status_code = 999))(URLencode(oembed_url))
  if (bq$status_code >= 400) {
    if (null_on_error) return(NULL)
    '<blockquote style="font-size: 90%">Sorry, unable to get tweet ¯\\_(ツ)_/¯</blockquote>'
  } else {
    httr::content(bq, "parsed")$html
  }
}
```

```{r, masonify_tweets}
masonify_tweets <- function(tweets, id = NULL, class = NULL) {
  stopifnot("status_id" %in% names(tweets))

  t_embed <-
    tweets %>%
    pmap(get_tweet_blockquote) %>%
    map(HTML) %>%
    map(tags$div, class = "tweet-item")

  tagList(
    tags$div(id = id,
             class = paste("masonry text-left", class),
             t_embed
    )
  )
}
```

```{r}
(status <- extract_tweet_status(t_pl))
(screen_name <- extract_tweet_screen_name(t_pl))

t_bq <- get_tweet_blockquote(status = status, screen_name = screen_name) %>% HTML()

t_bq
bslib::layout_column_wrap(1/3, t_bq, t_bq, t_bq, t_bq, t_bq)

```

# All sources

```{mermaid}
flowchart LR
  p[Permalink] -->|Extract Source| s[Source]
  s -->|Reddit| r[Reddit Embed]
  s -->|Instagram| i[Instagram Embed]
  s -->|Twitter| t[Twitter Embed]
  
```

```{r}
extract_source(t_pl)
extract_source(i_pl)
extract_source(r_pl)

i <- httr::GET(i_pl)
t <- httr::GET(t_pl)
r <- httr::GET(r_pl)

create_reddit_embed(r)

```

## Switch statement

# Shiny

Bones for doing it in a fluidPage, need to add tables/pagination...

```{r}
library(shiny)
library(bslib)
library(htmltools)


ui <- fluidPage(
  shiny::uiOutput(outputId = "embeddedTexts")
)


server <- function(input, output, session) {
  
  output$embeddedTexts <- shiny::renderUI({
    embeds <- lapply(1:12, function(i) {
      create_reddit_embed("https://www.reddit.com/r/redditdev/comments/16tqlth/updating_api_user_setting_fields/",
                          paste0("pl00h", i), "redditdev")
    })
    
    html_elements <- lapply(embeds, HTML)
    

    do.call(bslib::layout_column_wrap, c(width =1/3, html_elements))
    
  })
}

shinyApp(ui, server)
```


# Informal tests:

```{r}
r_pl <- "https://www.reddit.com/r/sales/comments/10x8sj9/even_gong_who_by_all_accounts_is_absolutely/j7rcv7m/"

i_pl <- "https://www.instagram.com/p/CpsCY26IhDW/"

t_pl <- "https://twitter.com/dilekarasoy/status/1637074142615805952"

r_e <- create_reddit_embed(r_pl)
t_e <- create_tweet_embed(t_pl)
i_e <- create_instagram_embed(i_pl)


bslib::layout_column_wrap(width = 1/3, i_e,r_e, r_e, i_e, t_e)

bslib::layout_column_wrap(width = 1/3, t_e, t_e, t_e)


bslib::layout_column_wrap(width = 1/3, t_e)
```

